### 2022-04-14 greta/mcmc.Rmd
scoring 1000 reps

set.seed(4242)
train_reps <- 10
train_t_max <- 250
test_t_max <- 250
test_reps <- 100

@@

```{r}
posterior_samples <- 
  bind_rows(map(draws, as_tibble)) %>% 
  sample_n(100)
posterior_sims <- posterior_samples %>%
  purrr::transpose() %>%
  map_dfr(function(q) simulate(t_max = test_t_max) ,.id = "i")

bind_rows(test, posterior_sims, .id = "model")|> 
  ggplot(aes(t, N, col=model, group=interaction(model,i))) +
           geom_line(alpha=0.3)

@@

# Score just the 1st replicate "true" observations
observed <- test |> filter(i == 1) |> pull(N)
scores(observed, dat)

```
```{r}
# score over all replicates:

rep_scores <- test |> group_by(i) |> group_map(~ scores(.x$N, dat)) |> bind_rows()
```

>>>>

set.seed(4242)
train_reps <- 10
train_t_max <- 250
test_t_max <- 250
test_reps <- 1000

@@

```{r}
## draw test_reps number of samples

posterior_samples <- 
  bind_rows(map(draws, as_tibble)) %>% 
  sample_n(test_reps)
posterior_sims <- posterior_samples %>%
  purrr::transpose() %>%
  map_dfr(function(q) simulate(t_max = test_t_max) ,.id = "i")

bind_rows(test, posterior_sims, .id = "model")|> 
  ggplot(aes(t, N, col=model, group=interaction(model,i))) +
           geom_line(alpha=0.1)

@@

```
```{r}
# score over all replicates:
bench::bench_time({
rep_scores <- 
  test |> 
  group_by(i) |> 
  group_map(~ scores(.x$N, dat)) |> 
  bind_rows()
})
```
